# Install SAGA and GDAL

This chapter shows how to install SAGA and GDAL on Windows for parallel computing through R.

## GDAL
This software tool is used for handling spatial data and is especially useful for exchanging/converting spatial data. To install GDAL on Windows go to http://www.gisinternals.com/release.php, click ```release-1900-x64-gdal-2-4-4-mapserver-7-4-3``` and download ```gdal-204-1900-x64-core.msi```. Follow installation steps via GDAL-installer. 
GDAL can be called from the command line in Rstudio. They can be linked by running this script on both Windows and Unix-systems:


```{r GDAL, eval=FALSE, include=TRUE}
if(.Platform$OS.type == "windows"){
  gdal.dir <- shortPathName("C:/Program files/GDAL")
  gdal_translate <- paste0(gdal.dir, "/gdal_translate.exe")
  gdalwarp <- paste0(gdal.dir, "/gdalwarp.exe") 
} else {
  gdal_translate = "gdal_translate"
  gdalwarp = "gdalwarp"
}
system(paste(gdalwarp, "--help")) #If done correctly, this will give help menu
```

Other functions and their directory can be added in the ‘if’-statement to use them. These can be found in the GDAL folder in Program Files. 

## SAGA
This program provides comprehensive GIS geoprocessing software with over 600 functions. To install, go to https://sourceforge.net/projects/saga-gis/ and download SAGA GIS by clicking the green button. Follow installation steps via SAGA-installer (7.6.3 is preferred).
SAGA GIS can also be called from the command line in Rstudio. They can be linked by running this script on both Windows and Unix-systems:

```{r SAGA, eval=FALSE, include=TRUE}
if(Sys.info()['sysname']=="Windows"){
  saga_cmd = "C:/#specify location here/saga_cmd.exe"
} else {
  saga_cmd = "saga_cmd"
}
system(paste(saga_cmd, "-v")) #If installed correctly, this will give version
```

Available functions and their command line arguments for your specific SAGA GIS version can be found here: http://www.saga-gis.org/saga_tool_doc/index.html.
